\chapter{   Deep Learning}
% CHAPTER SETTINGS
\graphicspath{{./images/computer_vision/}}

\section{Rgularization}

\subsection{Why do we use regularization?}
Regularization helps us control our model capacity, ensuring that our models are better at
making (correct) classifications on data points that they were not trained on, which we call the
ability to generalize. If we don’t apply regularization, our classifiers can easily become too complex
and overfit to our training data, in which case we lose the ability to generalize to our testing data
(and data points outside the testing set as well, such as new images in the wild).
However, too much regularization can be a bad thing. We can run the risk of underfitting, in
which case our model performs poorly on the training data and is not able to model the relationship
between the input data and output class labels (because we limited model capacity too much). For
example, consider the following plot of points, along with various functions that fit to these points.

addfigure starterbundle p.114




What we are doing here is looping over all entries in the matrix and taking the sum of squares.
The sum of squares in the L2 regularization penalty discourages large weights in our matrixW,
preferring smaller ones. Why might we want to discourage large weight values? In short, by
penalizing large weights, we can improve the ability to generalize, and thereby reduce overfitting.
Think of it this way – the larger a weight value is, the more influence it has on the output
prediction. Dimensions with larger weight values can almost singlehandedly control the output
prediction of the classifier (provided the weight value is large enough, of course) which will almost
certainly lead to overfitting.



\section{Activation Functions}